Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-10 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:10	15:44:37	(Mon10.Aug)
la2pdf commit - 2015:08:10	17:08:15	(Mon10.Aug)

- Why?

@@

% - How much oversampling
% - How many parameters, how great a span.
% 
% - Experiemental data, Holmengraa/cross
% 
% - Note on efficiency.
% 
% 
% From our work with MVDR it 
% 
% 
% Traditionally beamformers were static, but as processors get more powerful so with the emergence of more processing power

>>>>

% - Nature and scope
% - Past work
% - Methods
% - Brief summary results
% - Brief conclusions

\IEEEPARstart{P}{erhaps} greatest untapped potential of active sonar systems lies in making them adaptive. State-of-the-art here is found in nature, for instance in bats who use a high frequency sonar to detect, identify and track prey in caves in a chaos of other bats. They are masters at adapting their sonars to the scenario at hand, and act accordingly.

@@

% - How much oversampling
% - How many parameters, how great a span.
% 
% - Experiementl data, Holmengraa/cross
% 
% - Note on efficiency.
% 
% 
% From our work with MVDR it 
% 
% 
% Traditionally beamformers were static, but as processors get more powerful so with the emergence of more processing power
